%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

    \cventry
    {Software Developer}
    {Intrallect}
    {Edinburgh \& Glasgow, UK}
    {Aug 2020 - Present}
    {
        \begin{cvitems}
            \item {Work within a small team to produce a revolutionary new student hiring platform.}
            \item {Extended personal skill set through becoming a full-stack developer as requirements changed rapidly within a small team.}
            \item {Orchestrate and aid in multiple major version changes of multiple underlying core frameworks.}
            \item {Migrate platform to utilise industry-standard security protocols and platforms, including a custom authentication provider using proprietary voice biometrics.}
            \item {Replace a proprietary ChatBot tool with an open-source framework for AI engineering, which allowed the use of world-leading Large Language Models.}
            \item {Enforce strict automated quality control to ensure minimal tech-debt within the code and maintain a high level of code quality.}
            \item {Contribute fixes and improvements to open-source tools and libraries used within the platform.}
            \item {Integrate Elasticsearch to provide high quality and efficient searching for the platform, along with implementing both incremental and periodic bulk synchronisation between Elasticsearch and the platform's database.}
            \item {Implement sorting of potential candidates based on their skill set relative to a specific job, taking into account the quality of the candidate's provided proof of each skill, while allowing the weighting of quality metrics be determined on job-by-job basis.}
        \end{cvitems}
    }

    \cventry
    {Software Development Intern}
    {AT\&T}
    {Edinburgh, UK}
    {Jun 2019 - Aug 2019}
    {
        \begin{cvitems}
            \item {Joined a team building a new network operating system for routers as part of AT\&T's high speed network.}
            \item {Replaced an existing proprietary library with an open source alternative.}
            \item {Integrated the new library into the existing build system and CI pipeline.}
            \item {Extended a feature of the platform to allow for arbitrary implementations of an interface.}
            \item {Introduced a new command line interface to allow for the selection of implementations for the interface.}
        \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {Software Development Intern} % Job title
    {Cupris} % Organization
    {London, UK} % Location
    {Jul 2016 - Sept 2016} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Contributed to a pre-existing codebase, following predefined style and programming practices, such as Agile Programming.}
            \item {Introduced a new workflow to the platform by implementing a new administrative interface.}
            \item {Created a specification document, defining the new workflow, API endpoints and security considerations.}
            \item {Made use of Vaadin, Spring Boot, Spring Data and Spring Security.}
        \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {Junior Technician} % Job title
    {Parc Computer Centre / COR Solutions} % Organization
    {Hitchin, UK} % Location
    {Sep 2015 - Jul 2016} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Undertook a wide array of computer repair tasks for customers of varying complexity.}
            \item {Direct communication with customers about their issues, repair status and payment.}
            \item {Carried out routine maintenance of internal and customer computer systems.}
            \item {Utilised a range of operating systems and tools to carry out repairs.}
        \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
